Autonomous Quadrotor Landing on a Moving Platform

### 2016-04-20 docs/report/report.tex
updated report again

\section{Layout for Report}
\begin{itemize}
	\item Introduction
	\item Related work
	\item Hardware
	\item Software libraries used
	\item Methods
	\begin{itemize}
		\item camera methods (image processing)
		\item PID controllers
	\end{itemize}
	\item Results and Discussion
	\begin{itemize}
		\item Image Processing Results
		\item PID Results and Testing
		\item Hardware difficulties? 
	\end{itemize}
	\item Future work 
	\item Conclusion
\end{itemize}

\section{Introduction}
Over the years there has been been at least some interest in the problem of landing a quadrotor on a moving platform and there have been at least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012}. The problem has been explored from a fairly wide range of approaches.

Possible applications for this work include autonomous landing on a boat in high wind conditions, landing on a charging platform and more.

The major challenge with autonomous precision landing is the difficulty of obtaining a reliable estimate of the landing target relative to the quadrotor, the landing target can often go out of the camera's field of view causing the quadrotor to lose track of the target, other vision based artifacts that include lighting, lens distortion, color, etc.

@@

\section{Methodology}
The majority of effort in this project so far can be separated into two individual but complementary pieces. First, a significant effort effort was spent on ensuring the quadrotor's state was updated a a rate of at least 20 $Hz$. Next, using the information in the state  a set of PID controllers were developed that along with a state machine monitors the current relative position of the quadrotor and either initiates a landing procedure or attempts to minimize the relative displacement and velocity between the quadrotor and the landing pad in the horizonal plane.

@@

\subsection{Controller and State Monitoring}

@@

	\item PID/Control results 
	\begin{itemize}
		\item Plot XY for the controller loop
		\item Optimal PID settings
		\item How we got there
		\item Decent plot (V as a funtion of Z)
		\item Decent planner
		\item Video?
	\end{itemize}

\end{itemize}

\subsubsection{Detection Delay}
\begin{equation}
    t_{\text{capture}} = t - \delta t_{\text{camera}} + \delta t_{\text{detection}}
\end{equation}

>>>>

\section{Introduction}
Over the years there has been been a growing interest in autonomous landing of quadrotors as landing is often one of the most dangerous and risk prone parts of flight. There are now several commercial and research based implementations of autonomous landing with the DJI Phantom and Pixhawk flight controller both being capable of automatic landing using a series of sensors and control algorithms. However there does not yet seem to be a reliable method of landing a quadrotor on either a moving platform or in cases where there is relatively large cross wind disturbance.

In recent years there have been at least least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012} that approach the problem from a variaty of angles. Overall none of these approachs have solved the issue and most only work on very slow moving platforms with little or no wind disturbances. One of the most challenging with autonomous precision landing is the difficulty of obtaining a reliable estimate of the landing target relative to the quadrotor, the landing target can often go out of the camera's field of view causing the quadrotor to lose track of the target, other vision based artifacts that include lighting, lens distortion, color, etc.

@@

\section{Methodology}
The majority of effort in this project so far can be separated into two individual but complementary pieces. First, a significant effort effort was spent on ensuring the quadrotor's state was updated a a rate of at least 20 $Hz$. Next, using the information in the state  a set of PID controllers were developed that along with a state machine monitors the current relative position of the quadrotor and either initiates a landing procedure or attempts to minimize the relative displacement and velocity between the quadrotor and the landing pad in the horizontal plane.

@@

\subsection{Controller and State Monitoring}
In this project it is assumed that the quadrotor has successfully rendezvoused with the target vehicle and at all points in time has a clear view through the camera image of the landing target located on the target vehicle. The first step of performing  autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed with the target vehicle. Next, while maintaining the near zero displacements in the x and y directions, the quadrotor must begin to descend at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved. Ideally the quadrotor will descend more rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just before it hits the target in order to minimize time and energy requirements of the landing Vancouver.

In order to achieve the described behaviour, a set of 3 of PID controllers are developed, one for the x, y and z directions respectively. During all stages of landing the x and y PID controllers work to minimize the displacement between the target and the qaudrotor which also has the side effect of maintaining the velocity relative to the target. During the approach the PIDz controller attempts to maintain a safe approach altitude such that the target does not go out of view during stage one. Once a these hold displacement value in x and y is achieve the $PID_z$ controller is set a set of commands that smoothly move the quadrotor to a landing position.

The PIDx and PIDy are designed such that thier output is mapped to attitude commands in the pitch and roll relative to the quadrotor frame as outlined in Equations \ref{PIDx}, \ref{PIDy}, \ref{PIDz} . The commanded throttle is also adjusted to account for the commanded roll and pitch using Equation \ref{Adjusted Throttle} to better maintain altitude when $\phi_t$ and $\psi_t$ are non-zero.

\begin{equation}
\label{PIDx}
	\psi_t = cos(\theta) \left( K_p e_x + K_i \sum_{t=0}^{t} \dot{e_x}_{,t} dt + K_d \dot{e_x}_{,t}) \right)
\end{equation}

\begin{equation}
\label{PIDy}
	\phi_t = sin(\theta) \left( K_p e_y + K_i \sum_{t=0}^{t} \dot{e_y}_{,t} dt + K_d \dot{e_y}_{,t} \right)
\end{equation}

\begin{equation}
\label{PIDz}
	Thrust_z = K_p e_z + K_i \sum_{t=0}^{t} \dot{e_z}_{,t} dt + K_d \dot{e_z}_{,t} 
\end{equation}

\begin{equation}
\label{Adjusted Throttle}
	AdjustedThrust = \frac{Thrust_z}{cos(\phi_t) cos(\psi_t)}
\end{equation}

@@

	\item PID/Control results 
	\begin{itemize}
		\item Plot XY for the controller loop
		\item Optimal PID settings
		\item How we got there
		\item Decent plot (V as a function of Z)
		\item Video?
	\end{itemize}

\end{itemize}
\subsection{PID and Controller Results}

So far the PID behaviours and gains have only been evaluated using a MOCAP system and tested only relative to a stationary target and these results are discussed herein.

\section{Conclusion and Future Work}

\section{Proposed Future Work}
In the coming weeks, the PID controllers tested and developed using the MOCAP system will be tested using state estimates that are produced from the AprilTag library and the image preprocessing methods outlined in section \textbf{\textit{OUTLINE OF IMAGE PREPROCESSSING}}.

One major issue highlighted in Ling \cite{Ling2014} is that due to the relatively long processing time of the AprilTags library, the estimated state obtained at a time $t$ does not actually represent the current state due to a time lag. This time lag as outlined in \cite{Ling2014} and defined in \ref{Detection Delay} must be accounted for when using the camera to estimate state. Currently our proposed method to measure this lag is to use the MOCAP system to provide a ground truth for the state from which we can estimate the estimated state.

\begin{equation}
\label{Detection Delay}
    t_{\text{capture}} = t - \delta t_{\text{camera}} + \delta t_{\text{detection}}
\end{equation}

The next issue that will need to be address is the problem of the camera view. The dynamics of a quadrotor work in such a way that in order to move towards a goal point, the quadrotor must tilt away from the target which leads to problems with maintaining a view of the target when desired roll or pitch angles are greater than approximately 10 degress. This issue can either be addressed by mounting the camera at an angle or by adding a gimbals to the the quadrotor such that the gimbal will be sent commands by the onboard computer that will maintain a constant view of the target regardless of the commanded roll and pitch.

Both of the above solutions have significant implementation questions that will have to be answered. If using the fixed camera angle, then the yaw of the qaudrotor will need to be controlled by a PID controller, similar to the the PID controllers to the roll and pitch. In the case of significant wind, the quadrotor will need to rotate itself such that the front of the quad is pointed into the wind during the final decent.

If a gimbal is used there are two issues that arise. First a new set of controllers that send roll, pitch and yaw commands to the gimbal such that the camera it is attached to maintains a centred view of the target platform must be developed. These controllers will likely be similar to the PID controllers developed above and so they are not considered to be terrible difficult to define are implement. The more difficult part of using a gimbal is related to resuming the gimbal state, which in cheaper gimbals do provide. All of the gimbals that have been researched as part of this project do not provide state feedback and so they are considered to be open loop. Therefore in order to use such a gimbal the user will need to assume the commanded gimbal position is equal to the true gimbal position, from which a transform between the quad rotor and the gimbal can be made.
